Pillar 1 - Sequential Pattern Mining

### 2019-02-13 Pillar 1 - Sequential Pattern Mining.Rmd
debug

### Transcript with Preceding courses per student
```{r d_transcript_cum}

@@

```{r}

# lhs = course past
d_transcript_cum_current %>%
  filter(!is.na(course_past)) %>%
  unnest(
    course_past,
    .drop = FALSE
    ) %>%
  rename(
    lhs = course_past
    ) %>%
  count(
    lhs, 
    rhs,
    sort = TRUE
    )

@@

SR$taken <- sequences$taken %>%
  my_SR
```

@@

  my_SR %>%

@@

### not take -> fail
```{r}
# by hand
```

>>>>

### Transcript with preceding courses (for SR by hand)
```{r d_transcript_cum}

@@

@@

SR$taken <- sequences$taken %>%
  make_SR
```

@@

  make_SR %>%

@@

### not take -> fail
```{r}
